Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-03-22 Paper/Manuscript.tex
Replace hard-code refs with \citep's and fix some bib things

Active acoustics is an efficient method for remote sensing of marine ecosystems. These methods have been efficiently used to cover a wide range of spatial and temporal scales from the aquatic ecosystem, ranging from tens of km (Duane et al., 2021) to small scale behaviour patterns (Handegard et al., 2003). These methods are also a crucial component of fisheries resource management. Several different configurations of acoustic instruments are available, these include multibeam sonars, synthetic aperture sonar, omnidirectional sonars, acoustic imaging sonars as well as single- and multibeam echosounders (\hl{refs}).

Single-beam echosounders have extensively been used in fisheries management and ecosystem monitoring. Methodology for using these systems are well developed and in particular the ability for accurate calibration of the system has made these specially useful. Single-beam echosounders have provided important information for fisheries resource management (Simmonds and MacLennan, 2005) as well as insight in ecological processes for the aquatic ecosystem (Godø, 2014).

Conventional echosounders generate an acoustic pulse with a narrow bandwidth (several kHz at most), and the simultaneous operation at widely spaced frequencies (such as 18, 38, 70, 120, 200, and 333 kHz). The method has been used to  study predator-prey interactions (Benoit-Bird and Au, 2003; Friedlaender et al., 2009; Veit et al., 1993), interactions between marine organisms and the physical environment (Crawford et al., 2012; Freeman et al., 2004; Georgiadis et al., 2009; Ludsin et al., 2009; Godø, 2014), abundance and distribution of prey and predators (Thompson et al., 1991) and non-fish species or group of species (Brierley et al., 2001), and the individual or group behavior of marine organisms (Axelsen et al., 2000; Benoit-Bird et al., 2001; Kaartvedt et al., 2009).

Recent echosounders produce pulses with a wide and continuous frequency range (broadband pulses), as opposed to conventional single frequency systems, i.e. a continuous frequency coverage over a wide frequency band. This provides significantly better along-beam resolution and a higher signal to noise ratio than narrowband pulses (Chu and Stanton, 1998; Ehrenberg and Torkelson, 2000). These benefits can lead to improved backscatter categorization (R. Korneliussen, 2018; R. J. Korneliussen et al., 2016; Martin Traykovski et al., 1998; Stanton et al., 2012) and hence more accurate distribution and abundance estimates, as well as enhanced information on ecosystem structure and functioning. Early work with recent commercial systems indicate the potential improvement in detection near boundaries (Lavery et al., 2017) and remote sizing of fish (Kubilius et al., 2020;), capabilities of fine-scale observations of interactions between prey and predators (Skaret et al., 2020), the potential for species discrimination (Basset et al., 2018; Blanluet et al., 2019; Benoit-Bird and Waluk, 2020; Hasegawa et al., 2021; Gugele et al., 2021), and the potential for enhanced information on mesopelagic layers (Cotter et al., 2021; Agersted et al., 2021; Khodabandeloo et al., 2021a;2021b).

There have been several scientific broadband echosounder systems developed for laboratory use (Chu et al., 1992; Conti and Demer, 2003; Forland et al., 2014), some prototype or custom-made systems (Barr et al., 2002; Brise~no-Avena et al., 2015; Foote et al., 2005; Imaizumi et al., 2009; Simmonds et al., 1996; Zakharia et al., 1989, 1996) and some commercially available systems (Denny and Simpson, 1998; Ehrenberg and Torkelson, 2000; Gordon and Zedel, 1998; Stanton et al., 2010; Zedel et al., 2003).

@@

\section{Discussion}
The use of broadband signals in fisheries acoustics is a developing area and we anticipate many valuable enhancements will occur in the coming years. For example, the use of $\ts(\freqsym)$ and $\sv(\freqsym)$ to improve acoustic target classification \citep{bassett_broadband_2018, korneliussen2018}, and the potential of the high range resolution from pulse compression to observe small-scale fish behviours \citep{skaret2020} and to detect objects adjacent to boundaries \citep{lavery2017}. The basic formulation for calculating $\ts(\freqsym)$ and $\sv(\freqsym)$ presented here provides the foundation for future enhancements.

>>>>

Active acoustics is an efficient method for remote sensing of marine ecosystems. These methods have been efficiently used to cover a wide range of spatial and temporal scales from the aquatic ecosystem, ranging from tens of km \citep{duane_quantification_2021} to small scale behaviour patterns \citep{handegard_avoidance_2003}. These methods are also a crucial component of fisheries resource management. Several different configurations of acoustic instruments are available, these include multibeam sonars, synthetic aperture sonar, omnidirectional sonars, acoustic imaging sonars as well as single- and multibeam echosounders (\hl{refs}).

Single-beam echosounders have extensively been used in fisheries management and ecosystem monitoring. Methodology for using these systems are well developed and in particular the ability for accurate calibration of the system has made these specially useful. Single-beam echosounders have provided important information for fisheries resource management \citep{Simmonds2005Fisheries} as well as insight in ecological processes for the aquatic ecosystem (Godø, 2014).

Conventional echosounders generate an acoustic pulse with a narrow bandwidth (several kHz at most), and the simultaneous operation at widely spaced frequencies (such as 18, 38, 70, 120, 200, and 333 kHz). The method has been used to  study predator-prey interactions \citep{benoit-bird_prey_2003, friedlaender_diel_2009, veit_aggregation_1993}, interactions between marine organisms and the physical environment \citep{crawford_water_2012, freeman_diel_2004, georgiadis_coralligene_2009, ludsin_hypoxia_avoidance_2009} (+Godø, 2014), abundance and distribution of prey and predators \citep{thompson_winter_1991} and non-fish species or group of species \citep{brierley_acoustic_2001}, and the individual or group behavior of marine organisms \citep{axelsen_await_2000, benoit-bird_diel_2001, kaartvedt_use_2009}.

Recent echosounders produce pulses with a wide and continuous frequency range (broadband pulses), as opposed to conventional single frequency systems, i.e. a continuous frequency coverage over a wide frequency band. This provides significantly better along-beam resolution and a higher signal to noise ratio than narrowband pulses \citep{Chu1998Application, ehrenbergFMSlideChirp2000}. These benefits can lead to improved backscatter categorization \citep{korneliussen2018, Traykovski1998Effect, Stanton2012Resonance, Korneliussen2016Acoustic} and hence more accurate distribution and abundance estimates, as well as enhanced information on ecosystem structure and functioning. Early work with recent commercial systems indicate the potential improvement in detection near boundaries \citep{lavery2017} and remote sizing of fish \citep{kubilius_remote_2020}, capabilities of fine-scale observations of interactions between prey and predators \citep{skaret_diel_2020}, the potential for species discrimination \citep{bassett_broadband_2018, blanluet_characterization_2019, benoit-bird_exploring_2020} (+Hasegawa et al., 2021; Gugele et al., 2021), and the potential for enhanced information on mesopelagic layers \citep{cotter_classification_2021, agersted_application_2021, khodabandeloo_estimating_2021, khodabandeloo_mesopelagic_2021}.

There have been several scientific broadband echosounder systems developed for laboratory use \citep{Conti2003Wide-bandwidth, Forland2014Scattering, chu1992}, some prototype or custom-made systems \citep{Zakharia1989Wide-band, Zakharia1996Wideband, Simmonds1996Species, Foote2005Measuring, Imaizumi2009Detection, Briseno-Avena2015ZOOPS, Barr2002Target} and some commercially available systems \citep{Gordon1998FishMASS, Zedel2003Acoustic, Stanton2010New, ehrenbergFMSlideChirp2000, dennyBroadbandAcousticFish1998}.

@@

\section{Discussion}
The use of broadband signals in fisheries acoustics is a developing area and we anticipate many valuable enhancements will occur in the coming years. For example, the use of $\ts(\freqsym)$ and $\sv(\freqsym)$ to improve acoustic target classification \citep{bassett_broadband_2018, korneliussen2018}, and the potential of the high range resolution from pulse compression to observe small-scale fish behviours \citep{skaret_diel_2020} and to detect objects adjacent to boundaries \citep{lavery2017}. The basic formulation for calculating $\ts(\freqsym)$ and $\sv(\freqsym)$ presented here provides the foundation for future enhancements.
